\documentclass[a4paper,10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}

\usepackage{fontspec}
\setmainfont{Times New Roman}

\usepackage{geometry}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{array}
\usepackage{tabularx}

\usepackage{hyperref}
\usepackage{bookmark}
\usepackage{xurl}

\geometry{top=1.5cm, bottom=1.5cm, left=1.5cm, right=1.5cm} % Page margins
\setcounter{secnumdepth}{0}                                 % Remove section numbering
\setlist[itemize]{
    leftmargin=0.75em, % List indent (closer to page margin)
    itemsep=0.2em,     % Space between items
    topsep=0.25em,     % Space before/after list
    parsep=0em,        % Space between paragraphs in the same item
    partopsep=0em      % Extra space when starting the list
}

\pagestyle{empty}

\hypersetup{
    pdftitle={CV Kevin Castro},      % PDF title
    pdfauthor={Kevin Castro},        % PDF author
    colorlinks=true,          % Use color on links (no box)
    linkcolor=black,          % Internal link color
    urlcolor=black,           % URL color
    citecolor=black,          % Citation color
    bookmarksdepth=2          % Sidebar: section and subsection
}

\titleformat{\section}
{\Large\bfseries}
{}
{0em}
{}
[\titlerule\vspace{0.5ex}]
\titleformat{\subsection}
{\normalsize\bfseries}
{}
{0em}
{}
\titlespacing*{\subsection}{0pt}{0.35em}{0.15em}

\newcounter{cventry}
\newcommand{\cventry}[4]{%
    \refstepcounter{cventry}%
    \phantomsection%
    \pdfbookmark[2]{#1}{cventry-\thecventry}%
    \noindent\begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}X >{\raggedleft\arraybackslash}X@{}}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
    \end{tabularx}
}

\begin{document}

\begin{center}
    {\LARGE \textbf{Kevin Castro}}
    \\ [0.1cm]
    {\normalsize Mobile Developer}
    \\ [0.1cm]
    São Paulo, Brazil
    {\textbullet}
    \href{mailto:kevingcm.dev@gmail.com}{kevingcm.dev@gmail.com}
    {\textbullet}
    \href{https://linkedin.com/in/kevingcm}{linkedin.com/in/kevingcm}
    {\textbullet}
    \href{https://github.com/kevingcm}{github.com/kevingcm}
\end{center}

\section{Technical Skills}
    \begin{itemize}
        \item \textbf{Languages:} Portuguese (Native), English (C1)
        \item \textbf{Soft Skills:} Teamwork, Problem-solving, Attention to detail, Fast learner, Time management, Communication
        \item \textbf{Programming Languages:} Dart, Python, JavaScript, HTML, CSS, Kotlin, Swift
        \item \textbf{Frameworks:} Flutter
        \item \textbf{Tools:} Git, GitHub, PostgreSQL, Visual Studio Code, Figma
    \end{itemize}

\section{Education}
    \cventry{Instituto Federal de Rondônia}{Porto Velho, Brazil}{IT Technician}{2021 - 2023}
    \begin{itemize}
        \item \textbf{Relevant coursework:} HTML \& CSS, Python, JavaScript, Git \& GitHub, Object-Oriented Programming, Relational Databases \& SQL
    \end{itemize}

\section{Experience}
    \cventry{Kmon! Climb Club, Climbing App}{Self Project}{Full-Stack Architecture \& Product}{Apr 2026 - Present}
    \begin{itemize}
        \item Designed and built a full production app from scratch with Flutter + Supabase, managing 50+ database migrations and defining the entire data architecture.
        \item Implemented full Row-Level Security (RLS) in PostgreSQL, per-table access policies, and three-level privacy control.
        \item Built a full social graph with follows/followers, an activity feed, photo check-ins, and likes/comments.
        \item Built search with 250ms debounce, combined filters, and Google Maps integration displaying nearby locations via GPS.
    \end{itemize}

    \cventry{Instituto Federal de Rondônia}{Porto Velho, Brazil}{OOP Teaching Assistant}{Mar 2023 - Oct 2023}
    \begin{itemize}
        \item Provided daily online support to students on Python programming concepts and exercises, 7 days a week.
        \item Led in-person reinforcement sessions twice a week focused on exercise solving and programming logic development.
        \item Supported the teacher in reviewing assignments and projects, contributing to assessment quality.
    \end{itemize}

\end{document}
